---
title: "hw1"
author: "Fanfei Li"
date: "11/7/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Question 1
## (a)
```{r}
seq(-10,10)
```
## (b)
```{r}
(1:10)^2
```
## (c)
```{r}
q1<-seq(-10,10)
q2<-(1:10)^2
sum(q1)
sum(q2)
```

## (d)
```{r}
cumsum(q1)
cumsum(q2)
```
# Question 2 
You can calculate the length of the vectors seperately and add them together, or you could append the vectors to be a long vector, and then calculate the length. For example for vec1 as (1,2,3,4) and vec2 as (5,8,11):
```{r}
vec1<-c(1,2,3,4)
vec2<-c(5,8,11)
length(vec1)+length(vec2)
vec3<-c(vec1,vec2)
length(vec3)
```
# Question 3
## (a)
```{r}
Inf-Inf
```
## (b)
NaN means not a number, and is when a numerical expression is not defined, often produced by numerical computation. Whereas NA means not available, when a value of any type is missing.


## (c)
the third line of code returns the index i, where the ith element of x divided by the ith element of y returns an infinite result.

# Question 4
## (a)
```{r}
length(colors())
```
## (b)
```{r}
length(colors()[nchar(colors())>8])
```
# Question 5

```{r}
vec5 <- c(2,4,3,1,0,3)
indexname<-c(1:length(vec5))
names(vec5)<-indexname
strtoi(names(vec5[vec5==3]))
```
# Question 6
## (a)
```{r}
library(lubridate)
```
```{r}

mydays<-seq(as.Date("2016/1/1"), as.Date("2016/12/31"), "days")
mydays<-mydays[(weekdays(mydays)=="Saturday")]
mydays[mday(mydays)%%2==1]

```
## (b)
```{r}
birthday<-seq(as.Date("1950/11/25"), as.Date("2050/11/25"), "years")
birthday<-birthday[(weekdays(birthday)=="Thursday")]
birthday
```
## (c)
```{r}
firstday<-ymd("20181101")
firstday+(1:12)*months(3)
```


